A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-19 manuscript.Rmd
cite rmarkdown formats closes #85

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
author: Aaron Peikert and Andreas M. Brandmaier 
output:
  bookdown::pdf_document2:
    keep_tex: TRUE
repro:
  packages:
    - tidyverse
    - usethis
    - gert
    - aaronpeikert/repro@7bfaf98
    - here
    - rstudio/webshot2@f62e743
    - targets
    - renv
    - slider
    - patchwork
    - knitr
    - pander
    - lavaan
    - furrr
    - future.batchtools
  scripts:
    - R/simulation.R
    - R/simulation_funs.R
    - R/link.R
csl: apa7.csl
numbered_headings: true
bibliography: ["references.bib", "packages.bib"]
---

@@

```{r}
# define a ürint method for objects of the class data.frame
knit_print.data.frame = function(x, ...) {
  res = paste(c('', '', kable(x)), collapse = '\n')
  asis_output(res)
}
# register the method
registerS3method("knit_print", "data.frame", knit_print.data.frame)
```

@@

<!--Keep notes.-->
 A great tool to capture ideas or meeting notes is Markdown.
 Markdown is a lightweight text format that is very close to plain text with a minimal subset of reserved symbols for formatting instructions.
 This way, Markup does not need any specialized software for editing, it is highly fool-proof (unlike for example LaTeX) and can be ported to various document formats, such as HTML Websites, a Microsoft Word document, a typeset PDF file (for example, via LaTeX journal templates), or a Powerpoint presentation.
We suggest to use Markdown for everything, starting from simple sketches of your ideas to your scientific manuscripts and presentations---and even your CV [@vitae].
To create a Markdown document, click on:

@@

```{r, include=FALSE}
knitr::write_bib(c(.packages(), "gert", "bookdown", "lavaan", "knitr", "targets", "renv", "tidyverse"),
                 "packages.bib")
```

>>>>

---
title: "A Hitchhiker's Guide to Reproducible Research" # replace with something serious
author: Aaron Peikert and Andreas M. Brandmaier 
output:
  bookdown::pdf_document2:
    keep_tex: TRUE
repro:
  packages:
    - tidyverse
    - usethis
    - gert
    - aaronpeikert/repro@7bfaf98
    - here
    - rstudio/webshot2@f62e743
    - targets
    - renv
    - slider
    - patchwork
    - knitr
    - pander
    - lavaan
    - furrr
    - future.batchtools
    - rticles
  scripts:
    - R/simulation.R
    - R/simulation_funs.R
    - R/link.R
csl: apa7.csl
numbered_headings: true
bibliography: ["references.bib", "packages.bib"]
---

@@

```{r}
# define a print method for objects of the class data.frame
knit_print.data.frame = function(x, ...) {
  res = paste(c('', '', kable(x)), collapse = '\n')
  asis_output(res)
}
# register the method
registerS3method("knit_print", "data.frame", knit_print.data.frame)
```

@@

<!--Keep notes.-->
 A great tool to capture ideas or meeting notes is Markdown.
 Markdown is a lightweight text format that is very close to plain text with a minimal subset of reserved symbols for formatting instructions.
 This way, Markup does not need any specialized software for editing, it is highly fool-proof (unlike for example LaTeX) and can be ported to various document formats, such as HTML Websites, a Microsoft Word document, a typeset PDF file (for example, via LaTeX journal templates), or a Powerpoint presentation.
We suggest to use Markdown for everything, starting from simple sketches of your ideas to your scientific manuscripts[@R-rticles] and presentations[@revealjs]---and even your CV [@vitae].
To create a Markdown document, click on:

@@

```{r, include=FALSE}
knitr::write_bib(c(.packages(), "rticles", "gert", "bookdown", "lavaan", "knitr", "targets", "renv", "tidyverse"),
                 "packages.bib")
```
